Estimating duration in the presence of misclassification

### 2024-02-29 introduction.tex
fix labels
remove notes

\section{Data sources}

@@

\section{Estimating incidence and transmission} \cref{intro:sec:estimating-incidence}

@@

\todo[inline]{Rewrite with more clarity backcalculation background: do I need the equation? What is it in practice? What did I write in my first-year report, and what comments did it get?}

@@

The original formulations of backcalculation neglected the observation process.
AIDS is almost always diagnosed and recorded in developed countries.
That is, the observations of AIDS diagnoses are the same as the true incidence of AIDS.
An exception is that the reporting delay may be important~\autocite{paganoHIV}; but reporting delay is not important for this thesis's work.
Since its development, backcalculation has been further developed for a wide-variety of contexts.
\todo[inline]{probably need to cite some review or developments of backcalculation or give a brief lit review? not sure how much details is worthwhile as its not directly relevant}
% Reporting delay is not relevant to the studies in this thesis, and I ignore it in this and further discussion.

>>>>

\section{Data sources} \label{intro:sec:data-sources}

@@

\section{Estimating incidence and transmission} \label{intro:sec:estimating-incidence}

@@

@@

The original formulations of backcalculation neglected the observation process.
AIDS is almost always diagnosed and recorded in developed countries.
That is, the observations of AIDS diagnoses are the same as the true incidence of AIDS.
An exception is that the reporting delay may be important~\autocite{paganoHIV}; but reporting delay is not important for this thesis's work.
Since its development, backcalculation has been further developed for a wide-variety of contexts.
% Reporting delay is not relevant to the studies in this thesis, and I ignore it in this and further discussion.
